\clearpage
\urlstyle{rm}
\chapter*{Список использованных источников}
\label{references}
\addcontentsline{toc}{chapter}{Список использованных источников}

\begin{enumerate}
    \item Jazzer.js: Coverage-guided, in-process fuzzing for Node.js. URL: \url{https://github.com/CodeIntelligenceTesting/jazzer.js} (дата обращения: 27.05.2026).
    \item Jazzer and Jazzer.js. Code Intelligence. URL: \url{https://www.code-intelligence.com/jazzer-jazzer.js} (дата обращения: 27.05.2026).
    \item ESLint Security Plugin. URL: \url{https://www.npmjs.com/package/eslint-plugin-security} (дата обращения: 27.05.2026).
    \item SonarJS rules for ESLint. URL: \url{https://github.com/SonarSource/eslint-plugin-sonarjs} (дата обращения: 27.05.2026).
    \item JavaScript/TypeScript/CSS Analysis in SonarQube Server. URL: \url{https://docs.sonarsource.com/sonarqube-server/analyzing-source-code/languages/javascript-typescript-css} (дата обращения: 27.05.2026).
    \item Банк данных угроз безопасности информации ФСТЭК России. URL: \url{https://bdu.fstec.ru/threat} (дата обращения: 27.05.2026).
    \item MITRE Common Weakness Enumeration. URL: \url{https://cwe.mitre.org/data/definitions/699.html} (дата обращения: 27.05.2026).
    \item CWE-1333: Inefficient Regular Expression Complexity. URL: \url{https://cwe.mitre.org/data/definitions/1333.html} (дата обращения: 27.05.2026).
    \item CWE Top 25 Most Dangerous Software Weaknesses. URL: \url{https://cwe.mitre.org/top25/} (дата обращения: 27.05.2026).
    \item Анализ ошибок копирования. PVS-Studio. URL: \url{https://habr.com/ru/companies/pvs-studio/articles/112276/} (дата обращения: 27.05.2026).
    \item Различие CWE, CVE, CVSS. PVS-Studio. URL: \url{https://habr.com/ru/companies/pvs-studio/articles/580474/} (дата обращения: 27.05.2026).
    \item Manacher G. A New Linear-Time ``On-Line'' Algorithm for Finding the Smallest Initial Palindrome of a String // Journal of the ACM. 1975. Vol. 22, No. 3. P. 346--351.
\end{enumerate}
